---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# chartr

<!-- badges: start -->
<!-- badges: end -->

The goal of chartr is to ...

Helper

I am building a reusable `ggplot2` component in R that should be pipe-friendly (`data |> my_component(...)`), fully namespaced (`ggplot2::`, `dplyr::`, `rlang::`), and flexible for aesthetics, grouping, faceting, labels, stacking, orientation, colors, or theme options. The component should work on raw data (summarize/transform internally if needed), provide sensible defaults, fail clearly if inputs/columns are missing, and allow customization of legends, facets, labels, colors, and theme settings. Ensure all parameter combinations either work or fail clearly, support expressions like `as.factor(...)`, and keep code clean, modular, and readable.


# Next Steps

## 1. Organize Your Package Structure

## 2. Decide on Load Order (`Collate`)

## 3. Implement Shared Utilities

## 4. Add More Components Using the Factory

## 5. Add Argument Validation

## 6. Test Components Interactively

## 7. Prepare Documentation & NAMESPACE

## 8. Add Unit Tests

## 9. Optional Enhancements

## 10. Prepare for CRAN / Release



## Installation

You can install the development version of chartr from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("edgar-treischl/chartr")
```



```{r, eval=FALSE}
group_levels <- unique(data[[rlang::as_name(rlang::enquo(group))]])

# Check for unknown groups
unknown_groups <- setdiff(group_levels, names(fixed_colors))
if (length(unknown_groups) > 0) {
  stop("Unknown group(s) in data: ", paste(unknown_groups, collapse = ", "))
}

ggplot2::scale_fill_manual(values = fixed_colors[group_levels])
```


