---
title: "barcharts"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{barcharts}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```



Use the `bar_chart()` function to create bar charts with various customization options. You can specify the x and y aesthetics, grouping variables, stacking options, orientation, labels, titles, legend styling, and faceting options.

First, a minimal example:


```{r}
library(chartr)

# Minimal example
mtcars |>
  bar_chart(
    x = as.factor(cyl),
    y = mpg
  )
```


The `group` parameter allows you to create grouped bar charts.


```{r}
# Example with grouping
mtcars |>
  bar_chart(
    x = as.factor(cyl),
    y = mpg,
    group = as.factor(gear),
  )
```


The `stacked` parameter enables stacked bar charts.


```{r}
# Example with stacking
mtcars |>
  bar_chart(
    x = as.factor(cyl),
    y = mpg,
    group = as.factor(gear),
    stacked = TRUE
  )
```


Finally, the `horizontal` parameter allows you to create horizontal bar charts. Additionally, you can enable labels on the bars using the `show_labels` parameter.


```{r}
# Horizontal stacked bar chart with labels
mtcars |>
  bar_chart(
    x = as.factor(cyl),
    y = mpg,
    group = as.factor(gear),
    stacked = TRUE,
    horizontal = TRUE,
    show_labels = TRUE
  )
```


The next console shows an example using all available parameters. Please note that this is just an example, all parameters are optional and have default values.


```{r}
# All the defaults
mtcars |>
  bar_chart(
    # Data
    x = as.factor(cyl),
    y = mpg,
    
    # Grouping & Faceting
    group = as.factor(gear),
    facet = as.factor(am),
    
    # Bar styling
    stacked = TRUE,
    horizontal = FALSE,
    
    # Labels
    show_labels = TRUE,
    label_size = 3.5,
    
    # Titles and captions
    title = "Average MPG by Cylinder and Gear",
    x_label = "Cylinders",
    y_label = "Miles per Gallon",
    legend_title = "Gears",
    note = "Important note.",
    
    # Legend styling
    legend_position = "right",
    legend_direction = "vertical",
    
    # Facet options
    facet_scales = "fixed",   # fixed, free, free_x, free_y
    facet_ncol = 2
  )

```
